\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

Expense Manager is a comprehensive web-based personal finance management system designed to help individuals and organizations track, manage, and analyze their financial transactions effectively. Built using Java Server Pages (JSP), Servlets, and MySQL database, this application provides a robust platform for expense and income management with advanced reporting capabilities.

The system addresses the growing need for digital financial management tools by offering features such as user authentication, categorized transaction tracking, real-time dashboard analytics, and comprehensive reporting with export functionality. Users can securely register and login to access their personalized financial data, add and manage expense and income entries across various categories, and generate detailed reports with filtering options based on date ranges and transaction categories.

Key features include secure user authentication with SHA-256 password hashing, multi-user support with data isolation, intuitive web interface with responsive design, real-time financial summary calculations, and CSV export functionality for data portability. The system architecture follows the Model-View-Controller (MVC) pattern, ensuring separation of concerns and maintainability.

The application utilizes modern web technologies including HTML5, CSS3, and JavaScript for the frontend, while the backend is powered by Java Servlets and JSP for server-side processing. MySQL database ensures reliable data storage and retrieval with optimized queries for performance.

Testing has been conducted at multiple levels including unit testing, integration testing, and system testing to ensure reliability and functionality. The system demonstrates excellent performance in handling concurrent users and large datasets while maintaining data integrity and security.