\chapter*{REFERENCES}
\addcontentsline{toc}{chapter}{REFERENCES}

\begin{enumerate}

\item Oracle Corporation. (2023). \textit{Java Platform, Enterprise Edition Documentation}. Oracle Technology Network. Retrieved from https://docs.oracle.com/javaee/

\item Apache Software Foundation. (2023). \textit{Apache Tomcat 9.0 Documentation}. Apache Tomcat Project. Retrieved from https://tomcat.apache.org/tomcat-9.0-doc/

\item Oracle Corporation. (2023). \textit{MySQL 8.0 Reference Manual}. MySQL Documentation. Retrieved from https://dev.mysql.com/doc/refman/8.0/en/

\item Bergsten, H. (2003). \textit{JavaServer Pages (3rd Edition)}. O'Reilly Media. ISBN: 978-0596005634

\item Hunter, J., \& Crawford, W. (2001). \textit{Java Servlet Programming (2nd Edition)}. O'Reilly Media. ISBN: 978-0596000400

\item DuBois, P. (2013). \textit{MySQL Cookbook: Solutions for Database Developers and Administrators (3rd Edition)}. O'Reilly Media. ISBN: 978-1449374020

\item Flanagan, D. (2020). \textit{JavaScript: The Definitive Guide (7th Edition)}. O'Reilly Media. ISBN: 978-1491952023

\item Meyer, E. A. (2017). \textit{CSS: The Definitive Guide: Visual Presentation for the Web (4th Edition)}. O'Reilly Media. ISBN: 978-1449393199

\item Pilgrim, M. (2010). \textit{HTML5: Up and Running}. O'Reilly Media. ISBN: 978-0596806026

\item Apache Software Foundation. (2023). \textit{Apache Maven Project Documentation}. Apache Maven Project. Retrieved from https://maven.apache.org/guides/

\item Walls, C. (2020). \textit{Spring Boot in Action}. Manning Publications. ISBN: 978-1617294549

\item Richardson, C. (2018). \textit{Microservices Patterns: With Examples in Java}. Manning Publications. ISBN: 978-1617294549

\item Fowler, M. (2002). \textit{Patterns of Enterprise Application Architecture}. Addison-Wesley Professional. ISBN: 978-0321127426

\item Gamma, E., Helm, R., Johnson, R., \& Vlissides, J. (1994). \textit{Design Patterns: Elements of Reusable Object-Oriented Software}. Addison-Wesley Professional. ISBN: 978-0201633610

\item Beck, K. (2002). \textit{Test Driven Development: By Example}. Addison-Wesley Professional. ISBN: 978-0321146533

\item Martin, R. C. (2017). \textit{Clean Architecture: A Craftsman's Guide to Software Structure and Design}. Prentice Hall. ISBN: 978-0134494166

\item Krug, S. (2013). \textit{Don't Make Me Think, Revisited: A Common Sense Approach to Web Usability (3rd Edition)}. New Riders. ISBN: 978-0321965516

\item Nielsen, J. (1999). \textit{Designing Web Usability: The Practice of Simplicity}. New Riders Publishing. ISBN: 978-156205810X

\item OWASP Foundation. (2023). \textit{OWASP Top Ten Web Application Security Risks}. Open Web Application Security Project. Retrieved from https://owasp.org/www-project-top-ten/

\item W3C. (2023). \textit{Web Content Accessibility Guidelines (WCAG) 2.1}. World Wide Web Consortium. Retrieved from https://www.w3.org/WAI/WCAG21/quickref/

\item ISO/IEC. (2011). \textit{ISO/IEC 25010:2011 Systems and software engineering — Systems and software Quality Requirements and Evaluation (SQuaRE)}. International Organization for Standardization.

\item IEEE Computer Society. (2014). \textit{IEEE Std 830-1998 IEEE Recommended Practice for Software Requirements Specifications}. Institute of Electrical and Electronics Engineers.

\item Pressman, R. S., \& Maxim, B. R. (2019). \textit{Software Engineering: A Practitioner's Approach (9th Edition)}. McGraw-Hill Education. ISBN: 978-1259872976

\item Sommerville, I. (2015). \textit{Software Engineering (10th Edition)}. Pearson. ISBN: 978-0133943030

\item Silberschatz, A., Galvin, P. B., \& Gagne, G. (2018). \textit{Operating System Concepts (10th Edition)}. John Wiley \& Sons. ISBN: 978-1119320913

\item Elmasri, R., \& Navathe, S. B. (2015). \textit{Fundamentals of Database Systems (7th Edition)}. Pearson. ISBN: 978-0133970777

\item Connolly, T., \& Begg, C. (2014). \textit{Database Systems: A Practical Approach to Design, Implementation, and Management (6th Edition)}. Pearson. ISBN: 978-0132943260

\item Horstmann, C. S., \& Cornell, G. (2019). \textit{Core Java Volume I--Fundamentals (11th Edition)}. Prentice Hall. ISBN: 978-0135166307

\item Bloch, J. (2017). \textit{Effective Java (3rd Edition)}. Addison-Wesley Professional. ISBN: 978-0134685991

\item Oracle Corporation. (2023). \textit{Java Database Connectivity (JDBC) API Documentation}. Oracle Technology Network. Retrieved from https://docs.oracle.com/javase/8/docs/technotes/guides/jdbc/

\item Mozilla Developer Network. (2023). \textit{Web APIs and JavaScript Documentation}. Mozilla Foundation. Retrieved from https://developer.mozilla.org/en-US/docs/Web

\item Google Developers. (2023). \textit{Web Fundamentals: Performance}. Google LLC. Retrieved from https://developers.google.com/web/fundamentals/performance

\item Amazon Web Services. (2023). \textit{AWS Well-Architected Framework}. Amazon.com, Inc. Retrieved from https://aws.amazon.com/architecture/well-architected/

\item Microsoft Corporation. (2023). \textit{Azure Architecture Center}. Microsoft Corporation. Retrieved from https://docs.microsoft.com/en-us/azure/architecture/

\item Fowler, M. (2013). \textit{Refactoring: Improving the Design of Existing Code (2nd Edition)}. Addison-Wesley Professional. ISBN: 978-0134757599

\end{enumerate}